### 2024-03-25 course/statml/2024/project/project.tex
lecture07

\graphicspath{{img/}{../book.datasci/figures/}{../mySlides/figures/}}

@@

\lecture{Final Project}{Yuan Yao}{Due: 23:59 Monday 2 May, 2022}{23 Mar, 2022}

@@

How much camping gear will one store sell each month in a year? To the uninitiated, calculating sales at this level may seem as difficult as predicting the weather. Both types of forecasting rely on science and historical data. While a wrong weather forecast may result in you carrying around an umbrella on a sunny day, inaccurate business forecasts could result in actual or opportunity losses. In this competition, in addition to traditional forecasting methods you√ïre also challenged to use machine learning to improve forecast accuracy.

In this competition, you will use hierarchical sales data from Walmart, the world√ïs largest company by revenue, to forecast daily sales for the next 28 days and to make uncertainty estimates for these forecasts. The data, covers stores in three US States (California, Texas, and Wisconsin) and includes item level, department, product categories, and store details. In addition, it has explanatory variables such as price, promotions, day of the week, and special events. Together, this robust dataset can be used to improve forecasting accuracy.

@@

%You are provided with historical minute-level OHLCV data of 4 major cryto currencies‚ BTC, EOS, ETH, TRX. The raw data is downloaded through a web crawler, which contains information including OHLCV and number of trades. After preprocessing, the minute-bar data in the standard OHLCV format is obtained. 

@@

Ubiquant Investment (Beijing) Co., Ltd is a leading domestic quantitative hedge fund based in China. In this competition, you’ll build a model that forecasts an investment's return rate. Train and test your algorithm on historical prices. Top entries will solve this real-world data science problem with as much accuracy as possible. The dataset contains features derived from real historic data from thousands of investments. Your challenge is to predict the value of an obfuscated metric relevant for making trading decisions.

@@

>>>>

\graphicspath{{img/}}%{../book.datasci/figures/}{../mySlides/figures/}}

@@

\lecture{Final Project}{Yuan Yao}{Due: 23:59 Monday 29 April, 2024}{25 Mar, 2024}

@@

How much camping gear will one store sell each month in a year? To the uninitiated, calculating sales at this level may seem as difficult as predicting the weather. Both types of forecasting rely on science and historical data. While a wrong weather forecast may result in you carrying around an umbrella on a sunny day, inaccurate business forecasts could result in actual or opportunity losses. In this competition, in addition to traditional forecasting methods you're also challenged to use machine learning to improve forecast accuracy.

In this competition, you will use hierarchical sales data from Walmart, the world's largest company by revenue, to forecast daily sales for the next 28 days and to make uncertainty estimates for these forecasts. The data, covers stores in three US States (California, Texas, and Wisconsin) and includes item level, department, product categories, and store details. In addition, it has explanatory variables such as price, promotions, day of the week, and special events. Together, this robust dataset can be used to improve forecasting accuracy.

@@

%You are provided with historical minute-level OHLCV data of 4 major cryto currenciesâ BTC, EOS, ETH, TRX. The raw data is downloaded through a web crawler, which contains information including OHLCV and number of trades. After preprocessing, the minute-bar data in the standard OHLCV format is obtained. 

@@

Ubiquant Investment (Beijing) Co., Ltd is a leading domestic quantitative hedge fund based in China. In this competition, you'll build a model that forecasts an investment's return rate. Train and test your algorithm on historical prices. Top entries will solve this real-world data science problem with as much accuracy as possible. The dataset contains features derived from real historic data from thousands of investments. Your challenge is to predict the value of an obfuscated metric relevant for making trading decisions.

@@

%\newpage
%
%\section{Final Presentation}
%
%\begin{itemize}
%\item DI Yining, DING Hongxing, XU Meng, \emph{Traffic}, May 4
%\item CHU Zhuang, YANG Zilian, \emph{Reimaging}, 15mins May 4
%\item TAN Xiaoxiong, GUO Ziqing, Hei Chun LO, LIU Ning, \emph{Reimaging}, 20mins, May 4
%\item CHAN Wingchun, \emph{Asset}, May 4
%\item 
%\item LI Jiabao, ZHU Zhihan, \emph{Ubiquant}: 15mins, May 11
%\item XIE, Weiyan, WEI Yue, \emph{Diabetes Brain}: 20mins, May 11
%\item WEI, Xinyi and KUANG, Liangyawei, \emph{Credit}, May 11
%\end{itemize}
